A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-07-12 evaluation.tex
results

\subsection{Evaluation in \Ostrich{}}\label{}%
\Catra{} was experimentally integrated as the Parikh automata product solver for
an in-progress version of \Ostrich{} (which shares \Princess{} as the backing
theorem prover) with cost-enriched automata (CEFA). \Ostrich{} (\textit{sans}
CEFA) recently participated in the 2023~SMT-COMP, winning the single-query track
for quantifier-free strings (\texttt{QF\_S}) as well as the entire string
solving track on unsatisfiable instances~\cite{smt-comp-23}.

The \texttt{QF\_S} track contains no Parikh automata intersection problems,
however. For that, we need to look to the linear integer arithmetic
(\texttt{QF\_SLIA}), where \Ostrich{} did worse in SMT-COMP. The evaluations in
\cref{sec:scaling} use inputs generated by an older branch of CEFA-enriched
\Ostrich{} on the PyEx benchmarks, which are part of the set used in the
competition. In this section, we evaluated a version of \Ostrich{} using
\Catra{} as its back-end \Fudge{on StarExec, the same cluster SMT-COMP ran on}
on \numprint{1000}~randomly selected instances from the PyEx benchmarks. The
results are shown in comparison \Fudge{to the other provers of the 2023
competition on the same benchmarks, as well as \Ostrich{} using the baseline
back-end described in \cref{sec:implementing-baseline}}.

We include this section to show that \Calculus{} can be used to enhance the
performance of an automaton-based string solver with cost-enriched automata like
\Ostrich{}. However, significant engineering effort remains to bring the
integration to a state where it can participate in the full SMT-COMP.

\Fudge{RESULTS HERE PLEASE!}

>>>>

\subsection{Evaluation in \Ostrich{}}\label{}%

\begin{table}
  \begin{center}
  \input{graphs/solved_smt_comp.tex}
  \end{center}
  \caption{Number of solved benchmarks, on a subset of 1000
    PyEx benchmarks from SMT-COMP.}\label{tab:solve-status-smt-comp}
\end{table}

To evaluate the effectiveness of \Calculus{} in an actual string solver,
\Catra{} was experimentally integrated as the Parikh automata product solver
into the string solver \Ostrich{}~version~1.3. \Ostrich{} is an independently
developed solver that participated in the recent SMT-COMP~2023\footnote{\url{https://smt-comp.github.io/2023/participants/ostrich}},
 winning the single-query track
for quantifier-free strings (\texttt{QF\_S}), as well as dominating
other solvers on unsatisfiable string benchmarks~\cite{smt-comp-23}.

At SMT-COMP, \Ostrich{} competed using three different back-ends:
\begin{itemize}
\item \textbf{BW-Str:} a backward-propagation-based solver, not utilising
  Parikh automata~\cite{ostrich}.
\item \textbf{ADT-Str:} a solver based on algebraic data-types.
\item \textbf{CE-Str:} a re-implementation of the \OstrichPlus{}
  algorithm~\cite{ostrichplus}., using Parikh automata and a variant
  of our baseline method~\cite{generate-parikh-image}.
\end{itemize}

For our experiments, we modified the CE-Str solver to apply \Catra{}
instead of the previous baseline method, resulting in a new back-end
\textbf{CA-Str}.

As benchmarks, we again focused on the PyEx benchmarks~\cite{pyex}, of
which we picked 1000~problems uniformly at random. We ran the
different back-ends on those 1000~problems with a 120s timeout.
%
%The \texttt{QF\_S} track contains no Parikh automata intersection problems,
%however. For that, we need to look to the linear integer arithmetic
%(\texttt{QF\_SLIA}), where \Ostrich{} did worse in SMT-COMP. The evaluations in
%\cref{sec:scaling} use inputs generated by an older branch of CEFA-enriched
%\Ostrich{} on the PyEx benchmarks, which are part of the set used in the
%competition. In this section, we evaluated a version of \Ostrich{} using
%\Catra{} as its back-end \Fudge{on StarExec, the same cluster SMT-COMP ran on}
%on \numprint{1000}~randomly selected instances from the PyEx benchmarks. 
The results are shown in \cref{tab:solve-status-smt-comp}.
%
% comparison \Fudge{to the other provers of the 2023
%competition on the same benchmarks, as well as \Ostrich{} using the baseline
%back-end described in \cref{sec:implementing-baseline}}.

We include this section to show that \Calculus{} can be used to enhance the
performance of an automaton-based string solver with cost-enriched automata like
\Ostrich{}. The results should be considered as preliminary, however, 
as we believe that a deeper integration of our \Catra{} solver into
string solvers can lead to significant performance gains.
